






% Copyright (c) 2008, João Henrique Ferreira de Freitas
% All rights reserved.
% 
% Redistribution and use in source and binary forms, with or without modification,
% are permitted provided that the following conditions are met:
% 
%     * Redistributions of source code must retain the above copyright notice,
%       this list of conditions and the following disclaimer.
%     * Redistributions in binary form must reproduce the above copyright notice,
%       this list of conditions and the following disclaimer in the documentation and/or 
%       other materials provided with the distribution.
%     * Neither the name of the <ORGANIZATION> nor the names of its contributors may
%       be used to endorse or promote products derived from this software without 
%       specific prior written permission.
% 
% THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS" AND ANY 
% EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED WARRANTIES
% OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT
% SHALL THE COPYRIGHT OWNER OR CONTRIBUTORS BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL,
% SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT
% OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION)
% HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY,
% OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS
% SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
% 
% $Id$

\section{Anexo C: Licenças para contribuidores} \label{sec:anexoc}

\subsection{The Free Software Foundation Europe License}
A seguir, a licença para contribuidores é reproduzida na íntegra.
\begin{Verbatim}[frame=single, fontsize=\tiny, numbers=left, label=\url{http://www.bacula.org/en/?page=fsfe}]
   The Bacula project has assigned its copyright to the Free Software Foundation
   Europe e.V. in a fiduciary relationship that permits the FSFE to
   safeguard the Bacula software against abuse while allowing the project
   to continue without the administrative burden of maintaining the
   copyright paper work.

   If you contribute more than a few lines of code or documentation to the
   Bacula project, we ask you to complete the copyright Fiduciary License
   Agreement (link provided below).  This is the same agreement that I (Kern)
   and the other developers have signed to transfer our copyrights to the
   FSFE.

   Filling it out is really quite simple.  Please make two copies,
   then put your name and mailing address on the first page and
   date it.

   On the third page after "the author" put your name and the
   other information requested. This is simply to uniquely identify
   you.  
   
   If you are employed and you do Bacula work while at work
   or your employer has the rights to your work (often the case),
   please put your employer's information here.
   
   On the fourth page, you can simply put "All code and documentation
   contributed to the Bacula.org project" or if you wish to be more
   specific please do so.

   Thanks for taking the time to complete and send the FLA in.
\end{Verbatim}



